Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-19 ms.qmd
code at end

```{r}
  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + theme_classic() + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 24), 
                        legend.title = element_text(size = 26))
```

>>>>

```{r, fig-accl_time}
#| label: fig-accl_time
#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time within a study. Acclimation time is centered around the mean acclimation time in the data."

  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(colour)) +theme_classic() + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 24), 
                        legend.title = element_text(size = 26))
